Review of Manuscript ID: A18.08.0126

### 2018-10-08 papers/1_dmatpol/revision/paper-revision-1.tex
Revision of the paper submitted

%%
%%   Version 3.1 of 31 July 2018.
%%
\documentclass[aip,jcp,reprint,amsmath,amssymb,floatfix]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}

@@

$\delta {\bf D}$ from Eq.~\eqref{e:rho-1} should 
be directly related to the
polarization\hyp{}induced multipole moments because they are
a measure of the distortion of the electron density distribution due to the external electric
field. Therefore, as a starting point, the induced 
ground\hyp{}state electronic dipole moment of a closed\hyp{}shell molecule
will be considered,
%
\begin{equation} \label{e:dmu-exact}
 \delta {\BM{\upmu}}({\bf r}_Q) = 
     2 \Tr{ 
         \left[ 
              \delta {\bf D} \cdot {\mathbb{M}({\bf r}_Q)}
         \right] } \;,
\end{equation}
%
where ${\mathbb{M}({\bf r}_Q)}$ is atomic orbital (AO)\hyp{}representation
of the dipole moment operator defined with respect to origin at ${\bf r}_Q$,
%
\begin{equation}\label{e:m}
 \left[ {\mathbb{M}({\bf r}_Q)} \right]_{\alpha\beta} = -\tbraket{\alpha}{{\bf r} - {\bf r}_Q}{\beta} \;.
\end{equation}
%
(In this work the double struck font for matrices of vectors or higher\hyp{}order tensors is used, so that
in this case ${\mathbb{M}}$ can be considered as a $n \times n$ matrix of vectors of length 3).
Note that if the total charge is conserved, the induced moments are independent of the origin.

In the Hartree\hyp{}Fock theory,\cite{Roothaan.RevModPhys.1951} ${\bf D}$ is approximated as
%
\begin{equation}
 {\bf D} = {\bf C} \cdot {\bf C}^\dagger \;,
\end{equation}
%
where ${\bf C}$ describes the occupied molecular orbitals (MO's) as linear combinations
of AO's, referred here to as the LCAO-MO matrix.
${\bf D}$ is an idempotent matrix and if expressed in orthogonal basis the following holds
%
\begin{equation}
 {\bf D}^2 = {\bf D} \;.
\end{equation}
%
The change in the molecular orbitals can be parameterized as suggested by McWeeny\cite{McWeeny.RevModPhys.1960}
by defining the idempotency\hyp{}preserving variation
%
\begin{equation}
 \delta {\bf C} = {\BM\Delta} \cdot {\bf C}^{(0)} \;,
\end{equation}
%
where $\BM\Delta$ is a square non\hyp{}singular and non\hyp{}symmetric matrix.
McWeeny showed that
%
\begin{equation} \label{e:dmat-change.exact}
 \delta {\bf D} = -{\bf D}^{(0)} + \left[ {\bf D}^{(0)} + {\bf v} \right] \cdot
                                   \left[ {\bf 1} + {\bf v}^\dagger \cdot {\bf v} \right]^{-1} \cdot
                                   \left[ {\bf D}^{(0)} + {\bf v}^\dagger \right] \;,
\end{equation}
%
where the auxiliary vector ${\bf v}$ is defined as
%
\begin{equation}
 {\bf v} \equiv \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  \;.
\end{equation}
%
Expanding Eq.~\eqref{e:dmat-change.exact} in a Taylor series around ${\bf v}={\bf 0}$ and
truncating it at linear terms with respect to ${\BM\Delta}$ gives
%
\begin{subequations} 
 \begin{align}
 \delta {\bf D} &\cong \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)} + 
                        {\bf D}^{(0)} \cdot {\BM\Delta}^\dagger \cdot \left[ {\bf 1} - {\bf D}^{(0)} \right]  
 \label{e:dD-1} \\  &= 
  \delta {\bf C} \cdot {\bf C}^{(0)\dagger} + {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \nonumber \\
           &\qquad - {\bf D}^{(0)} \cdot \delta {\bf C} \cdot {\bf C}^{{(0)}\dagger} 
                   - {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \cdot {\bf D}^{(0)}  \;.
 \label{e:dD-2}
 \end{align}
\end{subequations}
%
The latter equality is true in a special case when the basis set functions are orthogonal, i.e., 
${\bf C}^{(0)\dagger} \cdot {\bf C}^{(0)}={\bf 1}$.
By substituting the McWeeny's result from Eq.~\eqref{e:dD-1}
into Eq.~\eqref{e:dmu-exact} one can show that
%
%\begin{multline} \label{e:dmu-4-exact.linear-approximation}
% \frac{1}{2} 
% \delta {\BM{\upmu}}({\bf r}_Q)
%  \cong
%   \Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  
%    \right] }
%%
%  +\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger}
%    \right] } \\
%%
%  -\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}
%    \right] }
%%
%  -\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger} \cdot {\bf D}^{(0)}
%    \right] } \;,
%\end{multline}
%%
%which can be recast to
%
\begin{equation}\label{e:dmu-l-vector}
 \frac{1}{4} 
 \delta {\BM{\upmu}}({\bf r}_Q)
  \cong
  \Re \left\{ 
 \Tr{ 
    \left[ 
         \delta {\bf C} \cdot \mathbb{L}({\bf r}_Q)
   \right] }  
  \right\} \;.
\end{equation}
%
In the above expression, the `$\Re$' symbol denotes the real part,
and the intermediate quantity
%
\begin{equation} \label{e:L-projector}
 \mathbb{L}({\bf r}_Q) \equiv {\bf C}^{(0)\dagger} \cdot \mathbb{M}({\bf r}_Q) \cdot \left( {\bf 1} - {\bf D}^{(0)} \right) \;.
\end{equation}
%
Note that $\mathbb{L}({\bf r}_Q)$ contains the projector onto
the unoccupied MO space at the absence of the external electric field. It means that the
perturbed solution is constructed from the unperturbed virtual orbitals as well.
%Note also the similarity between Eq.~\eqref{e:L-projector} and Eq.~\eqref{e:dmu-exact}.

@@

Once the approximate relationship between the orbital change and the external electric field
has been established in Eq.~\eqref{e:mu-ind.matrix.linear.solution},
one can obtain the final expression for the density matrix change 
that reproduces the induced dipole moment of the molecule.
The change in the LCAO\hyp{}MO coefficient is parameterized as
%
\begin{equation} \label{e:dC-dmatpol}
 \delta C_{\alpha i} = {\bf b}_{\alpha}^{(i;1)} \cdot {\bf F}({\bf r}_i)  \;,
\end{equation}
%
where the susceptibility tensor is defined as
%
\begin{equation} \label{e:susceptibility-b}
  b_{\alpha;w}^{(i;1)}= \frac{1}{4} \sum_u^{x, y, z} \left[ {\BM{\alpha}}_i \right]_{uw}
   \left[ \left[ {\bf L}_i  \right]^{-1}_{\rm Left} \right]_{u;\alpha}  
\end{equation}
%
for $w=x,y,z$. 
The superscript `$(1)$' underlines the fact that the susceptibility introduced here
is first\hyp{}order with respect to the electric field.
The result from Eq.~\eqref{e:dC-dmatpol} can be now inserted into 
the expression for $\delta {\bf D}$ from Eq.~\eqref{e:dD-2} to finally give
%
\begin{equation}\label{e:final-model.HF}
 \delta D_{\alpha\beta} \approx \sum_i^{\rm occ} {\bf B}^{(i;1)}_{\alpha\beta} \cdot {\bf F}({\bf r}_i)  \;,
\end{equation}
%
where the \emph{density matrix polarization susceptibility tensor} is
%
%\begin{multline}  \label{e:susceptibility-B} % PREPRINT
\begin{equation}  \label{e:susceptibility-B}
 {\bf B}^{(i;1)}_{\alpha\beta} = 
                               C_{\alpha i} {\bf b}_{\beta}^{(i;1)} + C_{\beta i} {\bf b}_\alpha^{(i;1)} %\\ PREPRINT
                                - \sum_\gamma 
                                 \left( 
               D_{\alpha\gamma} C_{\beta i} + D_{\beta\gamma} C_{\alpha i}
                                 \right)
                                           {\bf b}_{\gamma}^{(i;1)}
 \;.
\end{equation}
%\end{multline} % PREPRINT
%
Hence, the three dimensional vector ${\bf B}^{(i;1)}_{\alpha\beta}$ 
describes the local linear polarization affinity 
of the density matrix element 
associated with the $i$th LMO centroid as well as the $\alpha$th and $\beta$th orthogonal AO's.
Transforming these vectors to a non\hyp{}orthogonal AO basis is straightforward.
It is emphasized here that all the elements of ${\bf B}_{\alpha\beta}^{(i;1)}$
are unique properties of electronically unperturbed molecule. 
However, they are valid only under the Hartree\hyp{}Fock
approximation, with a guarantee that only the overall charge (exactly) and the dipole moment (approximately,
limited by the flavor of the distributed polarizability approximation), 
but not higher multipole moments and polarization energy, are correctly described.

@@

\subsection{\label{s:computational-cost}Computational cost and implementation of the DMS models}

Although the cost of computation of the perturbed one\hyp{}electron density matrices
from the DMS tensors and the distribution of the electric field is negligible, 
obtaining the generalized DMS matrix elements for a particular molecule
involves substantial amount of full QM calculations necessary to fit the DMS tensor elements.
This is, however, a relatively expensive operation that has to be performed only once.
%To get statistically relevant set of perturbed states, it is recommended to perform at least 100 
%full QM calculations. 
Since each of such preparatory calculations is an independent computational task, 
its automatization and parallelization is straightforward. Moreover, the implementation
of the method does not depend on the level of theory because only the perturbed density matrices
are needed. The computation of the gradient 
and Hessian matrix is inexpensive and its efficiency is limited only by the speed of Hessian matrix inversion.
Therefore, the method can be applied to all molecular fragments at any level of theory, provided
the one\hyp{}particle density matrices are available. In the illustrations shown in this work,
a set of 100 independent HF/6-311++G** calculations was sufficient to get statistically relevant set of perturbed 
ground state density matrices. This task was concluded within approximately 5 minutes per each DMS fit
on a single\hyp{}CPU computer.

>>>>

%%
%%   Version 3.1 of 31 July 2018.
%%
\documentclass[aip,jcp,preprint,amsmath,amssymb,floatfix]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}

@@

$\delta {\bf D}$ from Eq.~\eqref{e:rho-1} should 
be directly related to the
polarization\hyp{}induced multipole moments because they are
a measure of the distortion of the electron density distribution due to the external electric
field. Therefore, as a starting point, the induced 
ground\hyp{}state electronic dipole moment of a closed\hyp{}shell molecule
will be considered,
%
\begin{equation} \label{e:dmu-exact}
 \delta {\BM{\upmu}}({\bf r}_Q) = 
     2 \Tr{ 
         \left[ 
              \delta {\bf D} \cdot {\mathbb{M}({\bf r}_Q)}
         \right] } \;,
\end{equation}
%
where ${\mathbb{M}({\bf r}_Q)}$ is atomic orbital (AO)\hyp{}representation
of the dipole moment operator defined with respect to origin at ${\bf r}_Q$,
%
\begin{equation}\label{e:m}
 \left[ {\mathbb{M}({\bf r}_Q)} \right]_{\alpha\beta} = -\tbraket{\alpha}{{\bf r} - {\bf r}_Q}{\beta} \;.
\end{equation}
%
(In this work the double struck font for matrices of vectors or higher\hyp{}order tensors is used, so that
in this case ${\mathbb{M}}$ can be considered as a $n \times n$ matrix of vectors of length 3).
Note that if the total charge is conserved, the induced dipole moment is independent of the origin.

In the Hartree\hyp{}Fock theory,\cite{Roothaan.RevModPhys.1951} ${\bf D}$ is approximated as
%
\begin{equation}
 {\bf D} = {\bf C} \cdot {\bf C}^\dagger \;,
\end{equation}
%
where ${\bf C}$ describes the occupied molecular orbitals (MO's) as linear combinations
of AO's, referred here to as the LCAO-MO matrix.
${\bf D}$ is an idempotent matrix and if expressed in orthogonal basis the following holds
%
\begin{equation}
 {\bf D}^2 = {\bf D} \;.
\end{equation}
%
The change in the molecular orbitals can be parameterized as suggested by McWeeny\cite{McWeeny.RevModPhys.1960}
by defining the idempotency\hyp{}preserving variation
%
\begin{equation}
 \delta {\bf C} = {\BM\Delta} \cdot {\bf C}^{(0)} \;,
\end{equation}
%
where $\BM\Delta$ is a square non\hyp{}singular and non\hyp{}symmetric matrix.
McWeeny showed that
%
\begin{equation} \label{e:dmat-change.exact}
 \delta {\bf D} =  {\bf D}^{(0)} + \left[ {\bf D}^{(0)} + {\bf v} \right] \cdot
                                   \left[ {\bf 1} + {\bf v}^\dagger \cdot {\bf v} \right]^{-1} \cdot
                                   \left[ {\bf D}^{(0)} + {\bf v}^\dagger \right] \;,
\end{equation}
%
where the auxiliary vector ${\bf v}$ is defined as
%
\begin{equation}
 {\bf v} \equiv \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  \;.
\end{equation}
%
Expanding Eq.~\eqref{e:dmat-change.exact} in a Taylor series around ${\bf v}={\bf 0}$ and
truncating it at linear terms with respect to ${\BM\Delta}$ gives
%
\begin{subequations} 
 \begin{align}
 \delta {\bf D} &\cong \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)} + 
                        {\bf D}^{(0)} \cdot {\BM\Delta}^\dagger \cdot \left[ {\bf 1} - {\bf D}^{(0)} \right]  
 \label{e:dD-1} \\  &= 
  \delta {\bf C} \cdot {\bf C}^{(0)\dagger} + {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \nonumber \\
           &\qquad - {\bf D}^{(0)} \cdot \delta {\bf C} \cdot {\bf C}^{{(0)}\dagger} 
                   - {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \cdot {\bf D}^{(0)}  \;.
 \label{e:dD-2}
 \end{align}
\end{subequations}
%
The latter equality is true in a special case when the basis set functions are orthogonal, i.e., 
${\bf C}^{(0)\dagger} \cdot {\bf C}^{(0)}={\bf 1}$.
By substituting the McWeeny's result from Eq.~\eqref{e:dD-1}
into Eq.~\eqref{e:dmu-exact} one can show that
%
%\begin{multline} \label{e:dmu-4-exact.linear-approximation}
% \frac{1}{2} 
% \delta {\BM{\upmu}}({\bf r}_Q)
%  \cong
%   \Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  
%    \right] }
%%
%  +\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger}
%    \right] } \\
%%
%  -\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}
%    \right] }
%%
%  -\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger} \cdot {\bf D}^{(0)}
%    \right] } \;,
%\end{multline}
%%
%which can be recast to
%
\begin{equation}\label{e:dmu-l-vector}
 \frac{1}{4} 
 \delta {\BM{\upmu}}({\bf r}_Q)
  \cong
  \Re \left\{ 
 \Tr{ 
    \left[ 
         \delta {\bf C} \cdot \mathbb{L}({\bf r}_Q)
   \right] }  
  \right\} \;.
\end{equation}
%
In the above expression, the `$\Re$' symbol denotes the real part,
and the intermediate quantity
%
\begin{equation} \label{e:L-projector}
 \mathbb{L}({\bf r}_Q) \equiv {\bf C}^{(0)\dagger} \cdot \mathbb{M}({\bf r}_Q) \cdot \left( {\bf 1} - {\bf D}^{(0)} \right) \;.
\end{equation}
%
Note that $\mathbb{L}({\bf r}_Q)$ contains the projector onto
the unoccupied MO space at the absence of the external electric field. It means that the
perturbed solution is constructed from the unperturbed virtual orbitals as well.
%Note also the similarity between Eq.~\eqref{e:L-projector} and Eq.~\eqref{e:dmu-exact}.

@@

Once the approximate relationship between the orbital change and the external electric field
has been established in Eq.~\eqref{e:mu-ind.matrix.linear.solution},
one can obtain the final expression for the density matrix change 
that reproduces the induced dipole moment of the molecule.
The change in the LCAO\hyp{}MO coefficient is parameterized as
%
\begin{equation} \label{e:dC-dmatpol}
 \delta C_{\alpha i} = {\bf b}_{\alpha}^{(i;1)} \cdot {\bf F}({\bf r}_i)  \;,
\end{equation}
%
where the susceptibility tensor is defined as
%
\begin{equation} \label{e:susceptibility-b}
  b_{\alpha;w}^{(i;1)}= \frac{1}{4} \sum_u^{x, y, z} \left[ {\BM{\alpha}}_i \right]_{uw}
   \left[ \left[ {\bf L}_i  \right]^{-1}_{\rm Left} \right]_{u;\alpha}  
\end{equation}
%
for $w=x,y,z$. 
The superscript `$(1)$' underlines the fact that the susceptibility introduced here
is first\hyp{}order with respect to the electric field.
The result from Eq.~\eqref{e:dC-dmatpol} can be now inserted into 
the expression for $\delta {\bf D}$ from Eq.~\eqref{e:dD-2} to finally give
%
\begin{equation}\label{e:final-model.HF}
 \delta D_{\alpha\beta} \approx \sum_i^{\rm occ} {\bf B}^{(i;1)}_{\alpha\beta} \cdot {\bf F}({\bf r}_i)  \;,
\end{equation}
%
where the \emph{density matrix polarization susceptibility tensor} is
%
%\begin{multline}  \label{e:susceptibility-B} % PREPRINT
\begin{equation}  \label{e:susceptibility-B}
 {\bf B}^{(i;1)}_{\alpha\beta} = 
                               C_{\alpha i}^{(0)} {\bf b}_{\beta}^{(i;1)} + C_{\beta i}^{(0)} {\bf b}_\alpha^{(i;1)} %\\ PREPRINT
                                - \sum_\gamma 
                                 \left( 
               D_{\alpha\gamma} C_{\beta i}^{(0)} + D_{\beta\gamma} C_{\alpha i}^{(0)}
                                 \right)
                                           {\bf b}_{\gamma}^{(i;1)}
 \;.
\end{equation}
%\end{multline} % PREPRINT
%
Hence, the three dimensional vector ${\bf B}^{(i;1)}_{\alpha\beta}$ 
describes the local linear polarization affinity 
of the density matrix element 
associated with the $i$th LMO centroid as well as the $\alpha$th and $\beta$th orthogonal AO's.
Transforming these vectors to a non\hyp{}orthogonal AO basis is straightforward.
It is emphasized here that all the elements of ${\bf B}_{\alpha\beta}^{(i;1)}$
are unique properties of electronically unperturbed molecule. 
However, they are valid only under the Hartree\hyp{}Fock
approximation, with a guarantee that only the overall charge (exactly) and the dipole moment (approximately,
limited by the flavor of the distributed polarizability approximation), 
but not higher multipole moments and polarization energy, are correctly described.

@@

\subsection{\label{s:computational-cost}Computational cost and automatization of the generalized DMS model}

Although the cost of computation of the perturbed one\hyp{}electron density matrices
from the generalized DMS tensors and the distribution of the electric field is negligible, 
obtaining the generalized DMS tensors for a particular molecule
involves substantial amount of full QM calculations. %necessary to fit the DMS tensor elements.
This is, however, a relatively expensive operation that has to be performed only once
when the EFP\hyp{}like strategy is adopted. 
%Note that the DMS parameters 
%are environment\hyp{}independent and, due to this reason, could be used
%as effective fragment parameters.
%To get statistically relevant set of perturbed states, it is recommended to perform at least 100 
%full QM calculations. 
Note also that each of such preparatory calculations is an independent computational task, 
and hence, its automatization and parallelization is straightforward. Moreover, the implementation
of the method does not depend on the level of theory because only the perturbed density matrices
are needed. The least\hyp{}squares fit, i.e., the computation of the gradient
and Hessian matrix including its inversion, is inexpensive.
This step can be implemented in an independent script or program taking as input the
perturbed density matrices obtained by using any available quantum chemistry package. 
%and its efficiency is limited only by the speed of Hessian matrix inversion.
Therefore, the linear regression method to obtain the DMS tensors could be applied 
to any molecular fragment at a chosen level of theory
in a fairly black box manner, provided that
the one\hyp{}particle density matrices are available. In the illustrations shown in this work,
a set of 100 independent full QM calculations was sufficient to get statistically relevant set of perturbed 
ground state density matrices. 
%This task was concluded within approximately 5 minutes per each DMS fit
%on a single\hyp{}CPU computer.

### 2018-10-08 papers/1_dmatpol/revision/reply-letter-1.tex
Revision of the paper submitted

I would like to thank the Editor and two Reviewers for the time and insights given to my manuscript 
and for supporting the work to be published in \emph{J. Chem. Phys.}
I appreciate the positive and constructive feedbacks given, and agree with the reviewers’ 
suggestions for revisions. The reviewers’ comments have been fully addressed as outlined below. 
In addition, I have also introduced some minor adjustments in the notation.
Now, I hope that the revised manuscript is suitable for publication in \emph{J. Chem. Phys.}

@@

\begin{reply}
I definitely agree with the Reviewer that an additional illustration on some molecular
dimer would much increase the quality of the present manuscript. Unfortunately, as the Reviewer also
understands, this requires a separate article since other effects such as Pauli exchange-repulsion
need to be included and combined with polarization in order to compare to the full HF result. 
Due to this reason, I decided to write a separate manuscript on that issue in the future.
\end{reply}

@@

\begin{reply}

\end{reply}

@@

\begin{reply}
I agree with the remark, thanks. I changed the sentence to incorporate this:
\begin{quote}
Polarization under the uniform electric field is the simplest type of electrostatic perturbation
whereby it is possible to compute the exact DMS according to Eq.~(5)
\textbf{\noindent
by using either the coupled-perturbed Hartree-Fock method [P. R. Horn and M. Head-Gordon, \emph{J. Chem. Phys.} {\bf 143}, 114111 (2015).]
or numerical differentiation.}
\end{quote}
\end{reply}

>>>>

I would like to thank the Editor and two Reviewers for the time and insights given to my manuscript 
and for supporting the work to be published in \emph{J. Chem. Phys.}
I appreciate the positive and constructive feedback given, and agree with the Reviewers’ 
suggestions for revisions. The Reviewers’ comments have been fully addressed as outlined below. 
%In addition, I have also introduced some minor adjustments in the notation.
Now, I hope that the revised manuscript is suitable for publication in \emph{J. Chem. Phys.}

@@

\begin{reply}
I definitely agree with the Reviewer that an additional illustration on some molecular
dimer would much increase the quality of the present manuscript. On the other hand, as the Reviewer also
understands, this requires a more elaborate theoretical section since other effects such as Pauli exchange-repulsion
need to be included and combined with polarization in order to compare to the full HF result. 
After an attempt to extend the scope of this manucript by the above illustration,
I decided to write a separate manuscript on that issue in the future, because the additional
material would distract the reader from the key focus of this article and introduce more aspects
to be separately discussed (effects of exchange-repulsion and intermolecular charge transfer, 
the choice of definition of induction energy
within a dimer and so on). 
\end{reply}

@@

\begin{reply}
To discuss these aspects in more detail, I have added one subsection entitled
\emph{Computational cost and automatization of the generalized DMS model}
within the Results and Discussion section (IV.C) on Page 20.
\end{reply}

@@

\begin{reply}
Thanks. I changed the sentence on Page 14 as follows:
\begin{quote}
Polarization under the uniform electric field is the simplest type of electrostatic perturbation
whereby it is possible to compute the exact DMS according to Eq.~(5)
\textbf{\noindent
by using either the coupled-perturbed Hartree-Fock method [P. R. Horn and M. Head-Gordon, \emph{J. Chem. Phys.} {\bf 143}, 114111 (2015).]
or numerical differentiation.}
\end{quote}
\end{reply}
